---
title: "Q3-Andrew"
author: "Andrew Cheng"
date: "20/04/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(survey)
library(srvyr)
library(sampling)
library(tidyverse)
library(knitr)
library(kableExtra)
``` 

## Q3

```{r}
# ---- load data ----
# I think for the first two data sets, the variable name
# "Total_of_Ratings" should be "Average_of_Ratings" instead
dtB_overall<-read.csv("Employee_B_overall.csv")
dtB_bybrch<-read.csv("Employee_B_by_Branch.csv")
p<-as.matrix(read.csv("Employee_B_probs.csv", header=FALSE))

# change variable name
colnames(dtB_overall)[2]<- "Average_of_Ratings"
colnames(dtB_bybrch)[3]<- "Average_of_Ratings"
```

# Subtask 1
```{r}
## ---- sub task 1 ----
# we are using the number of observations as given in the tables
# i.e. N_pop=19406+9619+13629=42654
(N_pop<-19406+9619+13629)

dtB_overall$t_i<-(dtB_overall$Average_of_Ratings)*(dtB_overall$m_i) # cluster total

pi<-diag(p) # first order inclusion probabilities

# Now we estimate the population total using H-T estimator
sum(dtB_overall$t_i/pi)

# Hence the population mean is estimated to be 
# (we are using the number of observations as given in the tables)
(y_bar_HT<-sum(dtB_overall$t_i/pi)/(N_pop))

# Now we find the variance of the estimator for the total
tmp<-matrix(NA, 15, 15)
for (i in (1:15)){
  for (k in (1:15)){
    tmp[i,k]<-(p[i,k]-p[i,i]*p[k,k])/p[i,k]
  }
}

# H-T estimator of variance of H-T estimator for population total
(var_y_HT<-(t(dtB_overall$t_i/pi) %*% tmp %*% (dtB_overall$t_i/pi)) %>%
  as.numeric)

# hence we obtain estimated SE for population mean
(SE_y_bar_HT<-sqrt(var_y_HT)/N_pop)

# hence the 95% CI for the population mean is
y_bar_HT + qnorm(c(0.025, 0.975))*SE_y_bar_HT

```


We use the Horvitz-Thompson estimator in order to obtain an unbiased estimator. The explicit forms of the estimator and its (H-T) variance estimator being:

$$ \hat{\bar{y}}_{HT} = \sum_{i \in \mathcal{S}}\frac{1}{N_{pop}} \frac{t_i}{\pi_i}  $$

and

$$
\hat{V}_{HT}( \hat{\bar{y}}_{HT})
=\frac{1}{N_{pop}^2}
\left ( \sum_{i \in \mathcal{S}}\pi_i(1-\pi_i)\frac{t_i^2}{\pi_i^2}\frac{1}{\pi_i}
+\sum_{i \in \mathcal{S}}\sum_{k\neq i}(\pi_{ik}-\pi_i\pi_k)\frac{t_i}{\pi_i}\frac{t_k}{\pi_k} \right )
$$

where the $\pi_i$ denotes the marginal inclusion probability of the $i^{th}$ month as they appear in the overall data set and $\pi_{ik}$ denotes the joint inclusion probability of the $i^{th}$ and the $k^{th}$ month. Also $N_{pop} = 42,654$ denotes the total population size.  In practice, $\pi_i$'s were taken from the $i^{th}$ element along the principal diagonal of the given matrix in the file "Employee_B_probs.csv". 

From the code, we found the following value: 

$$ \hat{\bar{y}}_{HT} = 4.630348 $$

with a 95% confidence interval:
$$CI_{95}(\bar{y}_{HT}) =  (3.768300 ,\ 5.492396)$$
We see that this confidence interval is very wide. In particular, it covers impossible values that are greater than 5. This is perhaps because we are taking a cluster sample, which results in larger SE's than SRS.

# Subtask 2

```{r}
## ---- sub task 2 ----
N_h_brch<-c(19406, 9619, 13629) # population branch sizes


brch<-c("Disneyland_California",  
        "Disneyland_HongKong",  
        "Disneyland_Paris") # Branch names

# add a column of cluster totals to data frame
dtB_bybrch$t_i<-(dtB_bybrch$Average_of_Ratings)*(dtB_bybrch$m_i)

ssqr<-c(); t_hat<-c(); y_bar_hat<-c(); SE_y_bar_hat<-c()
for (h in 1:length(brch)){
  
  dtB.h <- dtB_bybrch %>% filter(Branch == brch[h]) # subsetting by Branch
  
  ssqr[h]<-t(dtB.h$t_i) %*% tmp %*% (dtB.h$t_i) # estimated variance of branch-specific total
  
  t_hat[h]<-sum(dtB.h$t_i/pi) # estimated branch total
  
  y_bar_hat[h]<-t_hat[h]/N_h_brch[h] # estimated branch average
  
  SE_y_bar_hat[h]<-sqrt(ssqr[h])/N_h_brch[h] # estimated SE
}

CI<-cbind(brch, 
          y_bar_hat %>% round(.,3),
          (y_bar_hat + qnorm(0.025))%>% round(.,3),
          (y_bar_hat + qnorm(0.975))%>% round(.,3)
)  %>% 
  data.frame() %>%
  format(., justify="left") 

colnames(CI)<-c("BRANCH",
                "Estimated average",
                "2.5%",
                "97.5%")
CI # 95% CI
```

It is important to realize that we are applying one-stage sampling. Thus the $\pi_i$'s remain the same. We can then partition the data into the three branches and then apply the Horvitz-Thompson estimator in Q3 subtask 1, to each branch. 

In other words, we have:

$$ \hat{\bar{y}}_{HT,k} = \sum_{i \in \mathcal{S_k}}\frac{1}{N_{pop}} \frac{t_i}{\pi_i}, \quad \quad  k \in \{\text{cali, HK, paris}\}  $$
The estimated variance is also calculated in a similar manner as described in Subtask1. From the code, we observe the obtained estimated averages are:

$$\hat{\bar{y}}_{HT,cali} = 4.829, \quad  \hat{\bar{y}}_{HT,HK} = 4.494, \quad \hat{\bar{y}}_{HT,paris} = 4.443$$
with the following confidence intervals:

$$CI_{95}(\bar{y}_{cali}) = (2.869, \ 6.789), \quad  CI_{95}(\bar{y}_{HK}) = (2.534	, \ 6.454), \quad  CI_{95}(\bar{y}_{paris}) = (2.483	, \ 6.403
)$$

Once again we obtain some very wide confidence intervals. This means that there is no evidence that the average rating is different between any two branches.